Stellar multiplicity

### 2018-05-08 article/ms.tex
dot points
actual dot points

\shorttitle{Short title}
\shortauthors{Casey et al.}

@@

\title{Binarity and other things in Gaia}

@@

% What is provided by Gaia?
% astrometric excess, number of measurements, brightness, etc
% what is the error model that Gaia uses?
% WE COULD USE A HIErARCHICAL MODEL FOR THE ERRORS
% Thus for a single star we would expect, so we can calculate
% p(\ra, \dec|data)

% For stars with a companion, if the companion is large enough to induce an effect on the primary then this would produce astrometric noise that would  be observable in the

% Astrometric model:

% Can we do this for DR1 already?

% When would we expect to see astrometric noise and not RV noise, and vice-versa? in what situations?

% we can calculate probability that it is consistent with a single  star,... p-value?

% From the Gaia expected error distributions: how many stars might we be able to discriminate between?

@@

>>>>

\shorttitle{Stellar multiplicity}
\shortauthors{Casey \& Hogg}

@@

\title{Stellar multiplicity}

@@

\begin{itemize}
\item The effect of binaries.

\item RV noise vs astrometric excess noise.

\item When would we expect to see astrometric noise and not RV noise, and vice-versa? in what situations?

\item Here we base our model using RV data only from Gaia DR2.

\item Some fraction of stars in Gaia are single star systems (or have such low semi-amplitudes that would not be detected by Gaia), and we will use those stars (within a mixture model) to calibrate the radial velocity error floor

\item We will do this on individual epoch measurements

\item ASSUMPTIONS

\item MODEL

\item CALIBRATION SAMPLE (including ADQL query)

\item Fitting the model:

\item Comparisons of residuals with other stellar properties.

\item What is the RV error that Gaia can measure in a single epoch for a given magnitude vs colour, etc.

\item What are the distributions of orbital parameters of binary systems that we would be able to detect?

\item Calculating a probability of binarity for every star, taking the non-measurements into account!

\item Completeness cuts,.... selection effects?

\end{itemize}

@@

\begin{itemize}

\item Binary fraction in the spaces that we were fitting: rp flux, colour, etc, just showing the transition of  probabilities

\item Binary fraction as a function of fitting properties, and other stellar properties from Gaia

\item Binarity across the H-R diagram

\item Binarity with metallicity

\item Binarity at height above the plane?

\item Binarity in clusters vs the plane?
\end{itemize}
